### 2016-04-14 templates/report/research/tex/articles.tex
NIRA-83 - Create a view to generate the citation names Created the generator of citation names.

{% if published_scientific or accepted_scientific or submitted_scientific or draft_scientific or published_dissemin or accepted_dissemin or submitted_dissemin or draft_dissemin or published_tec_trans or accepted_tec_trans or submitted_tec_trans or draft_tec_trans or published_scientific_in_event or accepted_scientific_in_event or published_dissemin_in_event or accepted_dissemin_in_event or published_tec_trans_in_event or accepted_tec_trans_in_event%}
	{% if published_scientific or accepted_scientific %}
\paragraph{Published or Accepted}
\begin{enumerate}
		{% if published_scientific %}
			{% for article in published_scientific %}
				{% if not article.article.hide %} \item{% if article.article.url %} \textbf{\href{ {{ article.article.url }} }{ {{ article.article.title }}.} }{% else %} {{ article.article.title }}.{% endif %}{% if article.article.ris_file_authors %}\textit{ {{ article.article.ris_file_authors }} }{{ article.article.periodical }},{% else %}\textit{ {{ article.article.authors }}.} {{ article.article.periodical }},{% endif %}{% if article.volume %}\textbf{ {{ article.volume }} }{% endif %}{% if article.number %} ({{ article.number }}),{% endif %}{% if article.start_page and article.end_page %} {{ article.start_page }}-{{ article.end_page }},{% endif %} {% if article.doi %}DOI: {{ article.doi }},{% endif %} {{ article.date|date:"Y" }}.{% endif %}
			{% endfor %}
		{% endif %}
		{% if accepted_scientific %}
			{% for article in accepted_scientific %}
				{% if not article.article.hide %} \item{% if article.article.url %} \textbf{\href{ {{ article.article.url }} }{ {{ article.article.title }}.} }{% else %} {{ article.article.title }}.{% endif %}{% if article.article.ris_file_authors %}\textit{ {{ article.article.ris_file_authors }} }{{ article.article.periodical }},{% else %}\textit{ {{ article.article.authors }}.} {{ article.article.periodical }},{% endif %} {{ article.date|date:"Y" }}, to appear.{% endif %}
			{% endfor %}
		{% endif %}
	{% endif %}

@@

{% endblock %}

>>>>

{% with lb="{" rb="}" %}

{% if published_scientific or accepted_scientific or submitted_scientific or draft_scientific or published_dissemin or accepted_dissemin or submitted_dissemin or draft_dissemin or published_tec_trans or accepted_tec_trans or submitted_tec_trans or draft_tec_trans or published_scientific_in_event or accepted_scientific_in_event or published_dissemin_in_event or accepted_dissemin_in_event or published_tec_trans_in_event or accepted_tec_trans_in_event%}
	{% if published_scientific or accepted_scientific %}
\paragraph{Published or Accepted}
\begin{enumerate}
		{% if published_scientific %}
			{% for article in published_scientific %}
				{% if not article.article.hide %} \item{% if article.article.url %} \textbf{\href{{ '{' }}{{ article.article.url }}{{ '}' }} }{ {{ article.article.title }}.} }{% else %} {{ article.article.title }}.{% endif %}{% if article.article.ris_file_authors %}\textit{ {{ article.article.ris_file_authors }} }{{ article.article.periodical }},{% else %}\textit{ {{ article.article.authors }}.} {{ article.article.periodical }},{% endif %}{% if article.volume %}\textbf{ {{ article.volume }} }{% endif %}{% if article.number %} ({{ article.number }}),{% endif %}{% if article.start_page and article.end_page %} {{ article.start_page }}-{{ article.end_page }},{% endif %} {% if article.doi %}DOI: {{ article.doi }},{% endif %} {{ article.date|date:"Y" }}.{% endif %}
			{% endfor %}
		{% endif %}
		{% if accepted_scientific %}
			{% for article in accepted_scientific %}
				{% if not article.article.hide %} \item{% if article.article.url %} \textbf{\href{ {{ article.article.url }} }{ {{ article.article.title }}.} }{% else %} {{ article.article.title }}.{% endif %}{% if article.article.ris_file_authors %}\textit{ {{ article.article.ris_file_authors }} }{{ article.article.periodical }},{% else %}\textit{ {{ article.article.authors }}.} {{ article.article.periodical }},{% endif %} {{ article.date|date:"Y" }}, to appear.{% endif %}
			{% endfor %}
		{% endif %}
	{% endif %}

@@

{% endwith %}
{% endblock %}
